Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/example.tex
Fix over-full column

From time to time, SW receives a message on \texttt{AutomationRequest},
forwarding it to a route planner (AI). The function of AI is to 
compute the flight path (a list of waypoints) for the UAV, outputting
the resulting \emph{mission command} on \texttt{AutomationResponse}.
The waypoint manager (WM) receives the mission command from AI and
starts the UAV flying the mission by putting an \emph{event} on the
\texttt{Start} output port, continuing to issue waypoints to the UAV
flight controller on the \texttt{Waypoint} port as the UAV location
updates with messages on \texttt{AirVehicleLocation}.
An event is repeatedly generated on \texttt{Alert} if there is no
mission command from a request. The AI component is third-party
software and WM is a legacy component.

@@

The contracts for the sub-components assume their inputs are
well-formed, and they guarantee their outputs are well-formed.  The AI
contract guarantees it only responds to automation requests and always
in the same cycle.  The legacy WM contract guarantees the following if
its input assumptions hold:
\begin{compactitem}
  \item it generates a start from a response from the AI and always in the same cycle;
  \item the start always coincides with a waypoint being output; and
  \item any further waypoints coincide with air vehicle location updates.
\end{compactitem}
These initial specifications pass AGREE verification, meaning that the
contract composition of the components with the system satisfies all
component input assumptions and system output guarantees.

>>>>

From time to time, SW receives a message on the \texttt{AutomationRequest} input,
forwarding it to a route planner (AI). The function of AI is to 
compute the flight path (a list of waypoints) for the UAV, outputting
the resulting \emph{mission command} on \texttt{AutomationResponse}.
The waypoint manager (WM) receives the mission command from AI and
starts the UAV flying the mission by putting an \emph{event} on the
\texttt{Start} output port, continuing to issue waypoints to the UAV
flight controller on the \texttt{Waypoint} port as the UAV location
updates with messages on \texttt{AirVehicleLocation}.
An event is repeatedly generated on \texttt{Alert} if there is no
mission command from a request. The AI component is third-party
software and WM is a legacy component.

@@

The contracts for the sub-components assume their inputs are
well-formed, and they guarantee their outputs are well-formed.  The AI
contract guarantees it only responds to automation requests and always
in the same cycle.  The legacy WM contract guarantees the following if
its input assumptions hold:
\begin{compactitem}
  \item it generates a start from a response from the AI and always in the same cycle;
  \item the start always coincides with a waypoint being output; and
  \item any further waypoints coincide with air vehicle location updates.
\end{compactitem}
These initial specifications pass verification, meaning that the
contract composition of the components with the system satisfies all
component input assumptions and system output guarantees.
